---
title: "Prelim Analysis"
author: "Jaffa Romain"
date: '2022-04-16'
output:
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
LIWCdata <- read_csv("~/Desktop/Global Classroom/LIWCAnalysis-no segmentation.csv")
LIWCpresentations <- read_csv("LIWC-22 Results - Presentations.csv")

LIWCdata <- LIWCdata %>% mutate(reflection = case_when(
  str_detect(Filename, 'Arbitration') ~ 'Arbitration Role Play', 
  str_detect(Filename, 'Union')~ 'Youth and Union', 
  str_detect(Filename, 'youth')~ 'Youth and Union', 
 str_detect(Filename, 'Barriers')~ 'Identifying Barriers',
  str_detect(Filename, 'Barrier')~ 'Identifying Barriers',
 str_detect(Filename, 'barriers')~ 'Identifying Barriers',
 str_detect(Filename, 'Debates') ~ 'Debates on Free Tuition and Universal Basic Income',
  str_detect(Filename, 'Tuition') ~ 'Debates on Free Tuition and Universal Basic Income',
   str_detect(Filename, 'tuition') ~ 'Debates on Free Tuition and Universal Basic Income',
 
  str_detect(Filename, 'Debate') ~ 'Debates on Free Tuition and Universal Basic Income',
 str_detect(Filename, 'debate')~ 'Debates on Free Tuition and Universal Basic Income',
 str_detect(Filename, 'debate')~ 'Debates on Free Tuition and Universal Basic Income',
  str_detect(Filename, 'Negotiation Preparation') ~ 'Negotiation Preparation', 
 str_detect(Filename, 'March')~'Women\'s March',
 str_detect(Filename, 'march')~'Women\'s March',
 str_detect(Filename, 'March') ~'Women\'s March') )

LIWCpresentations <- LIWCpresentations %>% mutate(reflection = "Presentation")

LIWCdata <- LIWCdata %>% filter(reflection != "Arbitration Role Play" & reflection != "Negotiation Preparation" & Filename != "negotiationgroup3employer_LATE_200017_17001476_mghc53 debate-1.pdf") 


exam_scores <- read_csv("~/Desktop/Global Classroom/LIWC-22 Results - c53 exam responses q1-2 - LIWC Analysis.csv")

exam_scores$reflection <- "Exam reflections"

chem_scores <- read_csv("~/Desktop/Global Classroom/Final Chem thesis + Reflections/LIWC-22 Results - Final Chem thesis + Reflection___ - LIWC Analysis.csv")

chem_scores <- chem_scores %>% mutate(reflection = "chemistry")
LIWCdata <- rbind(LIWCdata, exam_scores, chem_scores)

```

```{r}
LIWCpresentations <- LIWCpresentations  %>% rename(Filename = "Student") %>% select(-`...3`)

LIWCdata$Text <- NA

LIWCdata <- LIWCdata %>% dplyr::select(-Segment)
fulldata <- rbind(LIWCdata, LIWCpresentations)
management <- fulldata %>% filter(reflection != "chemistry")

write.csv(fulldata,"All_Reflections_Global_Classroom.csv", row.names = FALSE)

```


# Principal Component Analysis

- to reduce noise: removes redundant/useless variables 
- minimizes collinearity - reduces number of independent variables that are highly correlated to each other
- Varimax rotation
- eigenvalues greater than 1 (based on recommendations from other research data analyses)
- 
```{r, include=FALSE}
library(psych)
library(factoextra)

# remove unnecessesary linguistic variables (word count, number of adjectives, number of big words,etc)
PCAdata <- management%>% dplyr::select(-c(Filename, WC, prep, adverb, adj, det, Dic, WPS, BigWords, reflection, Text))
PCAdata2<- PCAdata[,apply(PCAdata, 2, function(x) all(x > 0))]
                   
PCA_scaled <- PCAdata2 %>% mutate_all(~scale(.) %>% as.vector)

 
# STANDARDIZE DATA
# to transform all variables to the same scale
# Average scores below the mean of 0 indicated that participants used fewer words and phrases from the word categories compared with the mean

# Factor scores that did not change significantly between the two writing assignments can be interpreted as representing whatever attitudes, experiences, or beliefs typical of participants that were unchanged by the educational intervention. 


###### Preliminary Diagnostic Checks ######
# Bartlett's test for  correlation matrix
cortest.mat(PCA_scaled)


####### squared multiple correlations (smc) #######
smc1= smc(PCA_scaled) # all > 0.3 - no factors need to be removed

#### outliers #####
outlier(PCA_scaled, plot=T, bad=10, na.rm=T) 


# Determining number of factors to extract
library(nFactors)
library(factoextra)
# common rule - atleast 70% of total variation explained with eigenvalues of at least 1
pca=prcomp(PCA_scaled)
# rotation - implement a prior shuffling of varimax rotation - better captures explained variance
summary(pca)


# scree - determined 4 key dimensions
fviz_screeplot(pca, type="lines", addlabels=TRUE, ylim = c(0, 80), main=" PCA Scree Plot"
               )
get_eig(pca)

# 5 is optimal

library(ggfortify)

# loadings


res.pc <-principal(PCA_scaled, nfactors=4, rotate="varimax")
# cronbach alpha 

library(FactoMineR)
res2 <- PCA(PCA_scaled, graph = FALSE, scale.unit = T)

loadings <-res2$var$cor # table with factor loadings


library(kableExtra)
vars = as.data.frame(res.pc$loadings)

vars = data.frame(matrix(as.numeric(res.pc$loadings), attributes(res.pc$loadings)$dim, dimnames=attributes(res.pc$loadings)$dimnames))

vars %>% kable(caption = "Correlations between Principal Components and the original scores.", digits = 2) %>% save_kable("tbl1.jpg")


loadings <- as.matrix.data.frame(res.pc$loadings)
colnames(loadings) <- c("PC1", "PC2", "PC3", "PC4")
rownames(loadings) <- colnames(PCA_scaled)

```

# ANOVA
```{r}
# setting up data - get reflection type and LIWC scores 
Files <- management$Filename
data <- cbind(Files, PCAdata2)
# reformat data
reflection_type <- management$reflection
data <- data %>% cbind(reflection_type)
```

```{r}
data_long = data %>% pivot_longer(!c(Files, reflection_type), names_to = "Variable", values_to = "score")
###################################################
library(rstatix)
data_long %>% filter(reflection_type == "Exam reflections") %>% group_by(reflection_type, Variable) %>% get_summary_stats(score, show =c("n", "mean", "sd"))


data_long <- data_long %>% filter(reflection_type != "Negotiation Preparation" & reflection_type !="Arbitration Role Play" & reflection_type != "chemistry")
# analytic
library(car)
dt <- data_long %>% filter(Variable == "work") 
summary(aov(score~reflection_type, data=dt))


```

# leadership survey
```{r}
lead<- read_csv("leadership-survey-c53.csv")

# filter out other classes to get C53 responses
lead <- lead %>% filter(Q3_6 == "MGHC53"| Q3_6 == "MGHC53H3")

```

Leadership plots
```{r}
library(ggthemr)
ggthemr('pale')
# demographics
firstup <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}
lead$Q19_1 <- tolower(lead$Q19_1) 
lead$Q19_1 <-firstup(lead$Q19_1) 


lead <- lead %>% mutate(age = ifelse(Q19_3 == "14", "21", Q19_3))
lead$age <- as.numeric(lead$age)


lead <- lead %>% mutate(Q19_2 = as.numeric(Q19_2))

lead <- lead %>% mutate(Ethnicity = case_when(Q8 == 1 ~ "Hispanic//Latino/", 
                     Q8 ==  2 ~ "White/Caucasian",        Q8 ==  3 ~ "Black//West Indian",
                     Q8 ==  4 ~ "Middle Eastern", Q8 == 5 ~ " South-East Asian", 
                     Q8 == 6 ~ "East-Asian",    Q8 == 7 ~ "Pacific-Islander",
                     Q8 ==  8 ~ "Native American",        Q8 == NA ~ "not recorded"))


# Questions to be car::recoded 

# 16, 19, 20
# reverse code questions with negative scoring so that positive attitudes reflect positive scoring
lead$Q24_1_16r = car::recode(lead$Q24_1_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_1_19r = car::recode(lead$Q24_1_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_1_20r = car::recode(lead$Q24_1_20, '1=5; 2=4; 3=3; 4=2; 5=1')

lead$Q24_2_16r = car::recode(lead$Q24_2_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_2_19r = car::recode(lead$Q24_2_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_2_20r = car::recode(lead$Q24_2_20, '1=5; 2=4; 3=3; 4=2; 5=1')

lead$Q24_3_16r = car::recode(lead$Q24_3_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_3_19r = car::recode(lead$Q24_3_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_3_20r = car::recode(lead$Q24_3_20, '1=5; 2=4; 3=3; 4=2; 5=1')


lead$Q24_4_16r = car::recode(lead$Q24_4_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_4_19r = car::recode(lead$Q24_4_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_4_20r = car::recode(lead$Q24_4_20, '1=5; 2=4; 3=3; 4=2; 5=1')


lead$Q24_5_16r = car::recode(lead$Q24_5_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_5_19r = car::recode(lead$Q24_5_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead$Q24_5_20r = car::recode(lead$Q24_5_20, '1=5; 2=4; 3=3; 4=2; 5=1')


# aggregate and average ratings from team members
lead$Q24_1_mean <- rowMeans(subset(lead, select = c(Q24_1_1, Q24_2_1, Q24_3_1, Q24_4_1, Q24_5_1)), na.rm = TRUE)
lead$Q24_2_mean <- rowMeans(subset(lead, select = c(Q24_1_2, Q24_2_2, Q24_3_2, Q24_4_2, Q24_5_2)), na.rm = TRUE)
lead$Q24_3_mean <- rowMeans(subset(lead, select = c(Q24_1_3, Q24_2_3, Q24_3_3, Q24_4_3, Q24_5_3)), na.rm = TRUE)
lead$Q24_4_mean <- rowMeans(subset(lead, select = c(Q24_1_4, Q24_2_4, Q24_3_4, Q24_4_4, Q24_5_4)), na.rm = TRUE)
lead$Q24_5_mean <- rowMeans(subset(lead, select = c(Q24_1_5, Q24_2_5, Q24_3_5, Q24_4_5, Q24_5_5)), na.rm = TRUE)
lead$Q24_6_mean <- rowMeans(subset(lead, select = c(Q24_1_6, Q24_2_6, Q24_3_6, Q24_4_6, Q24_5_6)), na.rm = TRUE)
lead$Q24_7_mean <- rowMeans(subset(lead, select = c(Q24_1_7, Q24_2_7, Q24_3_7, Q24_4_7, Q24_5_7)), na.rm = TRUE)
lead$Q24_8_mean <- rowMeans(subset(lead, select = c(Q24_1_8, Q24_2_8, Q24_3_8, Q24_4_8, Q24_5_8)), na.rm = TRUE)
lead$Q24_9_mean <- rowMeans(subset(lead, select = c(Q24_1_9, Q24_2_9, Q24_3_9, Q24_4_9, Q24_5_9)), na.rm = TRUE)
lead$Q24_10_mean <- rowMeans(subset(lead, select = c(Q24_1_10, Q24_2_10, Q24_3_10, Q24_4_10, Q24_5_10)), na.rm = TRUE)

lead$Q24_11_mean <- rowMeans(subset(lead, select = c(Q24_1_11, Q24_2_11, Q24_3_11, Q24_4_11, Q24_5_11)), na.rm = TRUE)
lead$Q24_12_mean <- rowMeans(subset(lead, select = c(Q24_1_12, Q24_2_12, Q24_3_12, Q24_4_12, Q24_5_12)), na.rm = TRUE)
lead$Q24_13_mean <- rowMeans(subset(lead, select = c(Q24_1_13, Q24_2_13, Q24_3_13, Q24_4_13, Q24_5_13)), na.rm = TRUE)
lead$Q24_14_mean <- rowMeans(subset(lead, select = c(Q24_1_14, Q24_2_14, Q24_3_14, Q24_4_14, Q24_5_14)), na.rm = TRUE)
lead$Q24_15_mean <- rowMeans(subset(lead, select = c(Q24_1_15, Q24_2_15, Q24_3_15, Q24_4_15, Q24_5_15)), na.rm = TRUE)
lead$Q24_16r_mean <- rowMeans(subset(lead, select = c(Q24_1_16r, Q24_2_16r, Q24_3_16r, Q24_4_16r, Q24_5_16r)), na.rm = TRUE)
lead$Q24_17_mean <- rowMeans(subset(lead, select = c(Q24_1_17, Q24_2_17, Q24_3_17, Q24_4_17, Q24_5_17)), na.rm = TRUE)
lead$Q24_18_mean <- rowMeans(subset(lead, select = c(Q24_1_8, Q24_2_18, Q24_3_18, Q24_4_18, Q24_5_18)), na.rm = TRUE)
lead$Q24_19r_mean <- rowMeans(subset(lead, select = c(Q24_1_19r, Q24_2_19r, Q24_3_19r, Q24_4_19r, Q24_5_19r)), na.rm = TRUE)
lead$Q24_20r_mean <- rowMeans(subset(lead, select = c(Q24_1_20r, Q24_2_20r, Q24_3_20r, Q24_4_20r, Q24_5_20r)), na.rm = TRUE)

# getting average scores for LBDQ scores (initiating structure and consideration)
lead$initiating_structure <- rowMeans(subset(lead, select = c(Q24_1_mean, Q24_2_mean, Q24_3_mean, Q24_4_mean, Q24_5_mean, Q24_6_mean, Q24_7_mean, Q24_8_mean, Q24_9_mean, Q24_10_mean), na.rm=T))
lead$consideration <- rowMeans(subset(lead, select = c(Q24_11_mean, Q24_12_mean, Q24_13_mean, Q24_14_mean, Q24_15_mean, Q24_16r_mean, Q24_17_mean, Q24_18_mean, Q24_19r_mean, Q24_20r_mean), na.rm=T))
##### check reliability ####

lead <- lead %>% mutate(Gender = case_when(Q18 == 1 ~ "Male", Q18 == 2 ~ "Female")) 

lead %>% ggplot(aes(x = Gender)) + geom_bar() + labs(title = "Management Class distribution by Gender")

lead %>% ggplot(aes(x = Ethnicity)) + geom_bar() + labs(title = "Management Class Distribution by Ethnicity")
library(janitor)
tabyl(lead$Ethnicity)
tabyl(lead$Gender)
library(ggcorrplot)


liwscores <- data %>% 
  separate(Files, into = c("name", "other"), sep=c("_"), extra = "merge") %>% dplyr::select(-other)


 fulldata <- liwscores %>%  separate(name, into = c("name", "other"), sep=" ", extra = "merge") %>% dplyr::select(-other) %>% filter(reflection_type != "Negotiation Preparation" & reflection_type !="Arbitration Role Play" & reflection_type != "chemistry")
 
 fulldata <- fulldata %>%  separate(name, into = c("name", "other"), sep="-", extra = "merge") %>% dplyr::select(-other) 
 
 lead$first_name = tolower(lead$Q3_2)
full<- fulldata%>% mutate(first_name = case_when(
  str_detect(name, 'yujie')~ 'yujie', 
  str_detect(name, 'sinuo')~ 'sinuo', 
  str_detect(name, 'miguel')~ 'miguel', 
 str_detect(name, 'yiming')~ 'yiming',
  str_detect(name, 'brian')~ 'brian',
 str_detect(name, 'samia')~ 'samia',
 str_detect(name, 'yunzi') ~'yunzi',
 str_detect(name, 'sandy') ~ 'sandy',
  str_detect(name, 'ami') ~ 'ami',
   str_detect(name, 'diyuan') ~ 'diyuan',
 str_detect(name, 'bada') ~ 'bada',
  str_detect(name, 'tim') ~ 'tim',
  str_detect(name, 'kosiha') ~ 'kosiha',
 str_detect(name, 'shayan')~ 'shayan',
 str_detect(name, 'xinyue')~  'xinyue') )


#full_data <- left_join(full, lead, by="first_name") 

#full_data <- full_data %>% filter(!is.na(first_name))
#full_data$`Task Leadership` <- full_data$initiating_structure
#full_data$`Interpersonal Leadership` <- full_data$consideration
# all_scores$Variable <- factor(all_scores$Variable, levels =c("Analytic","Cognition", "Clout", "Social", "Lifestyle", "Work", "Perception", "Space", "Tone", "Task Leadership", "Interpersonal Leadership"))

marks <- read_csv("2022-08-23T1700_Grades-MGHC53H3_F_LEC01.csv")
marks$Student <- tolower(marks$Student) 
marks <- marks %>% separate(Student, sep = ", ", into = c("other", "name"))  %>% select(-other) 

marks <-marks%>% mutate(first_name = case_when(
  str_detect(name, 'yujie')~ 'yujie', 
  str_detect(name, 'sinuo')~ 'sinuo', 
  str_detect(name, 'miguel')~ 'miguel', 
 str_detect(name, 'yiming')~ 'yiming',
  str_detect(name, 'brian')~ 'brian',
 str_detect(name, 'samia')~ 'samia',
 str_detect(name, 'yunzi') ~'yunzi',
 str_detect(name, 'sandy') ~ 'sandy',
  str_detect(name, 'ami') ~ 'ami',
   str_detect(name, 'diyuan') ~ 'diyuan',
 str_detect(name, 'iram') ~ 'bada',
  str_detect(name, 'iram') ~ 'bada',

  str_detect(name, 'tim') ~ 'tim',
  str_detect(name, 'kosiha') ~ 'kosiha',
 str_detect(name, 'shayan')~ 'shayan',
 str_detect(name, 'xin')~  'xinyue') )

final <- right_join(full, marks, by = "first_name")
write.csv(final,"Reflections and marks.csv", row.names = FALSE)

```


```{r}

library(reshape2)
library(dplyr)

# summary_df <- melt(df) %>% 
#   mutate(time = as.numeric(substr(variable, 2, 2))) %>%
#   transmute(ID, time, modality = as.factor(substr(variable, 3, 5)), 
#             score = value) %>%
#   group_by(modality, time) %>%
#   summarize(mean = mean(score), 
#             upper = mean + 1.96 * sd(score)/sqrt(length(score)),
#             lower = mean - 1.96 * sd(score)/sqrt(length(score)))
# 
# 
# ggplot(summary_df, aes(x = time, y = mean, colour = modality)) + 
#   geom_line(size = 1) + 
#   geom_point(aes(shape = modality), size = 3) +
#   geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, size = 1) +
#   theme_classic() +
#   scale_color_discrete(labels = c("Autonomic", "Motor", "Sensory")) +
#   scale_shape_discrete(labels = c("Autonomic", "Motor", "Sensory")) +
#   theme(legend.position = "bottom", text = element_text(size = 12)) +
#   labs(x = "Cycles", y = "Symptom score")
```

# bar graph
```{r}

# getting chem and management scores
chem_scores_dat <- chem_scores %>% select(Analytic,Cognition, Clout, Social, Lifestyle, work, Perception, space, Tone) %>% mutate(Course = "Chemistry")

management_scores <- LIWCdata %>% select(Analytic,Cognition, Clout, Social, Lifestyle, work, Perception, space, Tone)  %>% mutate(Course = "Management")

# combine to one data set
all_scores <- rbind(chem_scores_dat, management_scores)
all_scores <- all_scores %>% pivot_longer(-Course, names_to = "Variable", values_to = "score")

# aggregate scores based on dimensions
all_scores$Variable <- firstup(all_scores$Variable)
all_scores <- all_scores %>% mutate(var2 = case_when(Variable == "Analytic"~"Thinking",
Variable == "Cognition" ~"Thinking",
Variable == "Clout" ~ "Social Leadership",
Variable == "Social"  ~ "Social Leadership",
 Variable == "Lifestyle" ~  "Work and Lifestyle",
  Variable == "Work" ~  "Work and Lifestyle",
    Variable == "Perception"~"Experiential",
    Variable == "Space"~"Experiential",
    Variable =="Tone"~"Experiential"
))

all_scores$Variable <- factor(all_scores$Variable, levels =c("Analytic","Cognition", "Clout", "Social", "Lifestyle", "Work", "Perception", "Space", "Tone"))


library(ggsignif)

# bar plot
all_scores %>% group_by(Variable, Course) %>% mutate(mean = mean(score))  %>% 
ggplot(aes(x = Variable,  y = mean, fill = Course))  + geom_bar(position = "dodge", stat="identity") + labs(title = "", caption = "Percentage of words in student responses that fall into LIWC category.", x = "Dimension",  y ="Mean score")  + theme(legend.position = c(0.8, 0.8)) + ylim(0,105) +  scale_fill_manual(values = c("#5B965B","#E26B1C" )) +
  
  geom_signif(y_position = c(100,100), xmin = c(0.5,2.5), 
              xmax = c(2,4.3), annotation = c("Thinking","Social Leadership"),
              tip_length = .05)  +
  
  geom_signif(y_position = c(60,60), xmin = c(4.6,6.5), 
              xmax = c(6.4,9.5), annotation = c("Work & Lifestyle","Experiential"),
              tip_length = .05)



```


# correlation matrix plot
```{r}
chem_scaled <- chem_scores_dat %>% select(-c(Course))
chem_scaled <- chem_scaled %>% mutate_all(~scale(.) %>% as.vector)
chem_scaled$`Task Leadership` <- NA
chem_scaled$`Interpersonal Leadership` <- NA

full_data <- full_data %>% filter(reflection != "Exam reflections")
# compute correlation matrix
vals <- full_data %>% select(c(Analytic,Cognition, Clout, Social, Lifestyle, work, Perception, space, Tone,`Task Leadership`, `Interpersonal Leadership` ))

chemvals <- chem_scaled %>% select(c(Analytic,Cognition, Clout, Social, Lifestyle, work, Perception, space, Tone,`Task Leadership`, `Interpersonal Leadership` ))

allvals <- rbind(vals, chemvals)

allvals$Thinking <- rowMeans(subset(allvals, select = c(Analytic, Cognition)), na.rm = TRUE)


allvals$`Social Leadership` <- rowMeans(subset(allvals, select = c(Clout, Social)), na.rm = TRUE)


allvals$`Work and Lifestyle`  <- rowMeans(subset(allvals, select = c(Lifestyle, work)), na.rm = TRUE)


allvals$`Experiential`  <- rowMeans(subset(allvals, select = c(Perception, space, Tone)), na.rm = TRUE)

allvals <- allvals %>% select(c(`Experiential`, `Social Leadership`, `Work and Lifestyle`, Thinking,  `Interpersonal Leadership`, `Task Leadership`))

corr <-cor(allvals, use = "complete.obs") 


# p.mat <- cor_mat(allvals)
library(ggcorrplot)

ggcorrplot(corr, hc.order = TRUE, sig.level = 0.05, lab_size = 1.5, type = "lower", outline.col = "white", ggtheme = ggplot2::theme_classic, 
   colors = c("#6D9EC1", "white", "#E46726"))

```


# management scores by reflection
```{r}

man_data <- management %>% select(Analytic,Cognition, Clout, Social, Lifestyle, work, Perception, space, Tone, Filename, reflection) 



data_long = man_data %>% pivot_longer(!c(Filename, reflection), names_to = "Variable", values_to = "score")
data_long <- data_long %>% filter(reflection != "Negotiation Preparation" & reflection !="Arbitration Role Play" & reflection != "Exam Reflections")
###################################################
library(rstatix)
data_long %>% filter(reflection == "Presentation") %>% group_by(reflection, Variable) %>% get_summary_stats(score, show =c("n", "mean", "sd"))


# analytic
library(car)
dt <- data_long %>% filter(Variable == "Cognition") 
summary(aov(score~reflection, data=dt))


# tsummarized <- data_long %>% group_by(reflection_type, Variable) %>% summarize(score = mean(score)) %>% filter(Variable != "Cognition", Variable != "Linguistic", Variable != "Cognition", Variable != "socrefs") 
# 
# 
# ggplot(dtsummarized, aes(x=reflection_type, y=score, group=Variable)) +
#   geom_line(aes(linetype=Variable, color=Variable))+
#   geom_point(aes(color=Variable))+
#   theme(legend.position="top")
```

# Comparing pre - post presentations

```{r}
man_data <- final  %>% filter( reflection_type != "Exam reflections")


time_data <- man_data %>% mutate(Time = ifelse(reflection_type == "Presentation", "Presentation", "Pre-Presentation"))

time_data_long = time_data %>% pivot_longer(!c(name.x, reflection, Time), names_to = "Variable", values_to = "score")

library(ggplot2)

time_data_long %>%  ggplot(aes(x = Variable,  y = score, fill = Time))  + geom_bar(position = "dodge", stat="identity") + labs(title = "", caption = "Percentage of words in student responses that fall into LIWC categories by Reflection Time", x = "Dimension",  y ="Mean score")  + theme(legend.position = c(0.8, 0.8)) + ylim(0,105) + theme_classic()


####
# insert final grades
mod1 <- lm(`Assignm` ~ Clout + Social + Cognition + Analytic, data =  )
summary(mod1)


```


