---
title: "Global Classroom Analysis Writeup - 2024"
author: "Jaffa Romain"
date: "2024-04-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse);library(data.table);library(janitor);library(knitr);library(kableExtra);library(ggthemr); library(sjmisc); library(gtsummary);library(psych)

ggthemr('fresh')
```

# Summary Statistics 
## Class Composition
```{r class distribution, echo=F}
# 2022 Class
summary_vars = c("Name", "Ethnicity", "Gender", "English as Primary Language", "Major", "Year")

leadership_2022<- read_csv("globalclassroom code 2022 Winter/leadership-survey-c53.csv")
leadership_2022 <- leadership_2022 %>% mutate(Course = toupper(Course)) %>% filter(grepl("53", Course))
# need students from 2022 only 

leadership_2022 <- leadership_2022 %>% mutate(Name = paste(tolower(`Last Name`),sep = "", tolower(`First Name`))) %>% filter(!is.na(Name)) %>% mutate(Year = 2022)
class_2022 <-leadership_2022 %>% select(summary_vars) 

# 2023 Class
leadership_2023 <- read_csv("data - winter 2023/leadership.csv")%>% mutate(Name = paste(tolower(Q3_1),sep = "", tolower(Q3_2))) %>% rename("English as Primary Language" = Q20) %>% mutate (Year = "2023")
class_2023 = leadership_2023%>% select(summary_vars) 

# 2024 Class
leadership_2024 <- read_csv("data - winter 2024/Student Leadership Winter.csv")  %>% mutate (Year = "2024") 

# filtering to only include students from C53 course
leadership_2024 = leadership_2024%>% distinct(Name,.keep_all = T) %>% filter(!grepl("23", `Course Enrolled`))

class_2024 = leadership_2024 %>% select(summary_vars) 

summary_dat <- rbind(class_2022, class_2023, class_2024)
```

```{r, echo=FALSE}
################################### SUMMARY TABLES #################################################
summary_dat<- summary_dat%>% mutate(Ethnicity = 
case_when(Ethnicity == 1 ~ "Hispanic/Latino", Ethnicity ==  2 ~ "White/Caucasian",
          Ethnicity ==  3 ~ "Black", Ethnicity ==  4 ~ "Middle Eastern", 
          Ethnicity == 5 ~ "South-East Asian",  Ethnicity == 6 ~ "East-Asian",    
          Ethnicity == 7 ~ "Pacific Islander", Ethnicity ==  8 ~ "Native American",
          Ethnicity == "East-Asian (Chinese, Korean, Japanese)"~"East-Asian",
          Ethnicity == "Black/African-American/West Indian" ~ "Black",
          Ethnicity == "South-East Asian (e.g., Indian, Malay, Pakistani)" ~ "South-East Asian" ,
          Ethnicity == "Pacific-Islander (Filipino, Hawaiian)"~"Pacific Islander",
          Ethnicity == "White/Caucasian/European-American"~"White/Caucasian",
          Ethnicity == "Hispanic/Mexican American/Latino/Chicano" ~ "Hispanic/Latino",
        Ethnicity == "Middle Eastern (Arab, Iranian, Lebanese)"~"Middle Eastern")) %>% 
mutate(Sex = case_when(
  Gender == 1~"Male", Gender == 2~"Female", Gender == "Male"~"Male", 
  Gender == "Female"~"Female")) %>% 
mutate(`English as Primary Language?` = 
  case_when(`English as Primary Language` == 1 ~"Yes", `English as Primary Language` == 2 ~"No", 
            `English as Primary Language` == "Yes" ~ "Yes",`English as Primary Language` == "No" ~ "No" ))
summary_dat %>% select(-c(Name, Major, Gender)) %>% gtsummary::tbl_summary(by =Year) %>% as_gt() %>% gt::gtsave(filename = "summarystatistics.docx")
```


# Survey Responses - 2024
## Culinaria
```{r}
culsurv <- engagement_survey_Winter_2024 <- read_csv("data - winter 2024/engagement-survey Winter 2024.csv")

culsurv <- culsurv %>% filter(!is.na(`Last Name`))

# Food Neophobia Survey 
FNdat <- culsurv %>% select(matches("FN"))
FNdat <-  FNdat %>% pivot_longer(everything(),names_to = "Question", values_to = "Response") %>% filter(!is.na(Response))

# Social Dominance Survey 
SDO <- culsurv %>% select(matches("SDO"))
SDO <-  SDO %>% pivot_longer(everything(),names_to = "Question", values_to = "Response")%>% filter(!is.na(Response))
# plotting results
FNdat = sapply(FNdat, gsub, pattern = "FN - ", replacement= "")
FNdat %>%  ggplot(aes(x = Response)) + geom_bar() + facet_wrap(~Question,ncol = 1)
ggsave("FN_surveyres.png", width =10, height = 15)

SDO$Question = gsub(" - ","",SDO$Question)
SDO$Question = gsub("SDO ","",SDO$Question)
SDO$Question = gsub("SDO","",SDO$Question)
SDO$Question = gsub("SDO","",SDO$Question)
SDO$Question = gsub("Please indicate how strongly you favour or oppose the following statements:","",SDO$Question)


SDO %>%  ggplot(aes(x = Response)) + geom_bar() + facet_wrap(~Question,ncol = 1)
ggsave("SDO_surveyres.png", width =10, height = 15)

# Culinaria Feedback
cul_feedback = culsurv[,c(28:31)] %>% pivot_longer(everything(),names_to = "Question", values_to = "Response")%>% filter(!is.na(Response))
cul_feedback$Question = gsub("How much do you agree with the following statements about the Culinaria trip\\? - ","",cul_feedback$Question)
cul_feedback %>% ggplot(aes(x = Response)) + geom_bar() + facet_wrap(~Question,ncol = 1)

ggsave("cultrip_surveyres.png", width =10, height = 15)
```

# Student Assessments over time 
```{r, echo=F}
# 2022
ref_2022 <- read_csv("globalclassroom code 2022 Winter/All_Reflections_Global_Classroom.csv") %>% filter(reflection != "chemistry") %>% mutate(Year = 2022) 
ref_2022$Filename = gsub("_.+$","",ref_2022$Filename)
ref_2022$Filename = gsub(" .+$","",ref_2022$Filename)
ref_2022$Filename = gsub("-.+$","",ref_2022$Filename)
ref_2022 = ref_2022 %>% rename("Name" = Filename)
ref_2022 = ref_2022 %>% select(-c(Text))
ref_2022$reflection = gsub("Youth and Union","Youth & Unions",ref_2022$reflection)
ref_2022$reflection = gsub("Debates on Free Tuition and Universal Basic Income","Universal Basic Income & University Tuition",ref_2022$reflection)
ref_2022 = ref_2022 %>% filter(reflection!="Presentation"&reflection!="Arbitration Role Play")

# 2023
LIWC_ib_2023 <- read_csv("data - winter 2023/LIWC-ib-2023.csv") %>%mutate(reflection = "Identifying Barriers")
LIWC_t_2023 <- read_csv("data - winter 2023/LIWC tuition 2023.csv") %>%mutate(reflection = "Universal Basic Income & University Tuition")
LIWC_yu_2023 <- read_csv("data - winter 2023/LIWC yu 2023.csv") %>%mutate(reflection = "Youth & Unions")
LIWC_wm_2023 <- read_csv("data - winter 2023/LIWC wm 2023.csv") %>%mutate(reflection = "Women's March")
LIWC_final_2023 <- read_csv("data - winter 2023/LIWC-22 final2023.csv") %>%mutate(reflection = "Final Exam")

ref_2023 = rbind(LIWC_ib_2023, LIWC_t_2023, LIWC_wm_2023, LIWC_yu_2023, LIWC_final_2023)

ref_2023$Filename = gsub(", ","",ref_2023$Filename)
ref_2023$Filename = gsub(",","",ref_2023$Filename)
ref_2023$Filename = gsub(".docx","",ref_2023$Filename)

ref_2023 <- ref_2023 %>% rename("Name" = Filename) %>% select(-c(Segment, Emoji))%>% mutate(Year = 2023) 

# 2024
ref_2024 <- read_csv("data - winter 2024/LIWC_res_2024.csv") %>% 
  select(-c(Segment, Emoji))%>% filter(reflection != "Arbitration Role Play")%>% mutate(Year = 2024) 

full_liwc_data = rbind(ref_2022, ref_2023, ref_2024)
```

##PCA Analysis
```{r}
# remove unnecessesary linguistic variables (word count, number of adjectives, number of big words,etc)
pca_analysis<- function(dt){
PCAdata <- dt
PCAdata2<- PCAdata[,apply(PCAdata, 2, function(x) all(x > 0, na.rm=T))]
                   
PCA_scaled <- PCAdata2 %>% mutate_all(~scale(.) %>% as.vector) 

# STANDARDIZE DATA
# to transform all variables to the same scale
# Average scores below the mean of 0 indicated that participants used fewer words and phrases from the word categories compared with the mean

###### Preliminary Diagnostic Checks ######
# Bartlett's test for  correlation matrix
cortest.mat(PCA_scaled) 
# Determining number of factors to extract
library(nFactors)
library(factoextra)
# common rule - atleast 70% of total variation explained with eigenvalues of at least 1
pca=prcomp(PCA_scaled)


# scree - determined 4 key dimensions
print(fviz_screeplot(pca, type="lines", addlabels=TRUE, ylim = c(0, 80), main=" PCA Scree Plot" ))
library(ggfortify)

# loadings


res.pc <-principal(PCA_scaled, nfactors=4, rotate="varimax")
# cronbach alpha 

library(FactoMineR)
res2 <- PCA(PCA_scaled, graph = T, scale.unit = T)

loadings <-res2$var$cor # table with factor loadings


library(kableExtra)
vars = as.data.frame(res.pc$loadings)
vars = data.frame(matrix(as.numeric(res.pc$loadings), attributes(res.pc$loadings)$dim, dimnames=attributes(res.pc$loadings)$dimnames))
vars %>% kable(caption = "Correlations between Principal Components and the original scores.", digits = 2)
loadings <- as.matrix.data.frame(res.pc$loadings)
colnames(loadings) <- c("PC1", "PC2", "PC3", "PC4")
rownames(loadings) <- colnames(PCA_scaled)
loadings
}
```
### 2022
```{r}
full2022 = full_liwc_data %>% filter(Year == 2022) %>% dplyr::select(-c(Name, WC, prep, adverb, adj, det, Dic, WPS, BigWords, reflection,Year,auxverb,verb,Linguistic))
pca_analysis(full2022)
```
### PCA Scree Plot Interpretation

- **Variance Explained**:
  The first two components explain a significant portion of the variance. PC1 accounts for 27.7% and PC2 for 21.8%.
- 4 components account for 77.8% of variation in data

- **Elbow Point**:
  The scree plot's "elbow" point seems to be around the 4th -5th components, indicating that most of the significant variance is within these components. 
- 4 dimensions chosen for dimensionality reduction

The factor loadings represent the correlations between the original variables and each principal component.

- **PC1**:
  - This component has strong positive loadings for "Cognition" and "cogproc," suggesting a focus on cognitive-related factors.
  - The negative loading for "Analytic" suggests an inverse relationship with the other positively correlated variables.

- **PC2**:
  - High positive loadings for "Clout," "Social," and "socrefs" indicate this component likely represents social or authority-related aspects.
  - The correlation between these variables suggests that this component might reflect interpersonal dynamics or social interaction.

- **PC3**:
  - High positive loadings for "Lifestyle" and "work," suggesting that this component is strongly influenced by lifestyle or work-related patterns.
  - This component captures a specific aspect of the data, focusing on everyday life and work.

- **PC4**:
  - Strong positive loadings for "Perception" and "space" suggest this component might represent perceptual or spatial factors.
  - The negative loadings for Tone suggest potential inverse relationships with this component.

### 2023
```{r}
full2023 = full_liwc_data %>% filter(Year == 2023) %>% dplyr::select(-c(Name, WC, prep, adverb, adj, det, pronoun, `function`, AllPunc, article, Dic, WPS, BigWords, reflection,Year,auxverb,verb,Linguistic,Period))
pca_analysis(full2023)


```
### PCA Scree Plot Interpretation

- The first two components explain a significant portion of the variance in the dataset. PC1 accounts for approximately 29.6%, while PC2 accounts for about 19.2%. The cumulative variance explained by the first four components is about 65.4%.
Elbow Point:
The "elbow" in the plot appears around the 4th-5th components, indicating that most significant variance is within these components.

- 4 components account for 73.5% of variation
Factor Loadings Interpretation

PC1:
The strong positive loadings for "Clout", "Social", "Drives", and "socrefs" indicate that this component represents social-related factors, such as authority and interpersonal interaction.
PC2:
The high positive loadings for "Cognition," and "cogproc" suggest that this component focuses on analytical and cognitive-related factors.
The negative loading for "Analytic" indicates an inverse relationship between this variable and other positively loaded variables.
PC3:
High positive loadings for "Authentic" and "Perception", "Space", and negative "Affect" suggest that this component might represent authenticity and perceptual and positive tone aspects.
PC4:
Strong positive loadings for "Lifestyle" and "work" indicate this component represents lifestyle or work-related factors.
The negative loading for "Analytic" suggests an inverse relationship between this variable and the other positively loaded variables.

### 2024
```{r}
full2024 = full_liwc_data %>% filter(Year == 2024) %>% drop_na() %>% dplyr::select(-c(Name, WC, prep, adverb, adj, det, Dic, WPS, BigWords, pronoun, `function`, number, reflection,Year,auxverb,verb,Linguistic, Comma, AllPunc, ppron))
pca_analysis(full2024)
```

### PCA Scree Plot Interpretation
- PC1 is extremely dominant, explaining 43.2% of the variance in the data.
- PC2 explains 19.7%, still a substantial amount but less than half of PC1's contribution.
PC3 accounts for 14.2%, 
- total variation explained: 77%
- seems that the variance explained by successive components drops significantly after PC1 and begins to level off after PC4, 
elbow seen after PC3


PC1:
"Lifestyle" and "work" have very high loadings on this component, suggesting that PC1 may be capturing aspects related to personal and professional life aspects of the data set.

PC2:
"Clout," "Drives" load strongly here, suggesting PC2 may represent aspects of leadership, and perhaps professional drive.

PC3:
"Tone" and "Affect" show high loadings, implying PC3 may be capturing emotional expression or sentiment.

PC4:
"Analytic" has a very high positive loading on this component, while "Authentic" has a high negative loading


### Plots based on PCA dimensions
```{r long format data, include=FALSE}
firstup <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}
data_year_longer <- function(dat, year){
  dat %>% filter(Year == year) %>% pivot_longer(!c(Name, reflection), names_to = "Variable", values_to = "Score")
}

full2022long <- data_year_longer(full_liwc_data, 2022) 
full2023long <- data_year_longer(full_liwc_data, 2023)
full2024long <- data_year_longer(full_liwc_data, 2024)
full2022long$Variable <- firstup(full2022long$Variable)
full2023long$Variable <- firstup(full2023long$Variable)
full2024long$Variable <- firstup(full2024long$Variable)

# for graphing dimensions by assessment
assessments_by_dimension <- function(dat){
dat %>% ggplot(aes(x=reflection,y=Score, color = Dimension)) + stat_summary(aes(group = Dimension), fun=mean, geom = "line") +  stat_summary(aes(group = Dimension), fun=mean, geom = "point") + 
labs(x="Assessment",y="Mean Dimension Score") + theme(legend.position = "right", axis.text.x = element_text(angle = 30,hjust = 1))}

# bar plot of scores by dimension
scores_by_dimension <- function(dat, pc1, pc2, pc3, pc4, xmin11, xmin12, xmax11, xmax12, xmin21, xmin22, xmax21, xmax22){
  dat %>% group_by(Variable) %>% mutate(mean = mean(Score))  %>% 
ggplot(aes(x = Variable,  y = mean))  + geom_bar(position = "dodge", stat="identity") + labs(title = "", caption = "Percentage of words in student responses that fall into LIWC category.", x = "Dimension",  y ="Mean score")  + theme(legend.position = c(0.8, 0.8)) + ylim(0,105) +
  
  geom_signif(y_position = c(100,100), xmin = c(xmin11,xmin12), 
              xmax = c(xmax11, xmax12), annotation = c(pc1,pc2),
              tip_length = .05)  +
  
  geom_signif(y_position = c(60,60), xmin = c(xmin21,xmin22), 
              xmax = c(xmax21,xmax22), annotation = c(pc3,pc4),
              tip_length = .05)}

assessments_by_dimension <- function(dat){
dat %>% ggplot(aes(x=reflection,y=Score, color = Dimension)) + stat_summary(aes(group = Dimension), fun=mean, geom = "line") +  stat_summary(aes(group = Dimension), fun=mean, geom = "point") + 
labs(x="Assessment",y="Mean Dimension Score") + theme(legend.position = "right", axis.text.x = element_text(angle = 30,hjust = 1))}

# bar plot of scores by dimension
scores_by_dimension_by_group <- function(dat, pc1, pc2, pc3, pc4, xmin11, xmin12, xmax11, xmax12, xmin21, xmin22, xmax21, xmax22){
  dat %>% group_by(Variable) %>% mutate(mean = mean(Score))  %>% 
ggplot(aes(x = Variable,  y = mean))  + geom_bar(position = "dodge", stat="identity") + labs(title = "", caption = "Percentage of words in student responses that fall into LIWC category.", x = "Dimension",  y ="Mean score")  + theme(legend.position = c(0.8, 0.8)) + ylim(0,105) +
  
  geom_signif(y_position = c(100,100), xmin = c(xmin11,xmin12), 
              xmax = c(xmax11, xmax12), annotation = c(pc1,pc2),
              tip_length = .05)  +
  
  geom_signif(y_position = c(60,60), xmin = c(xmin21,xmin22), 
              xmax = c(xmax21,xmax22), annotation = c(pc3,pc4),
              tip_length = .05)}



```
2022 
```{r}
library(ggsignif)

full2022long <- full2022long %>% mutate(Dimension = case_when(Variable == "Analytic"~"Thinking",
Variable == "Cognition" ~"Thinking", Variable == "Clout" ~ "Social Leadership",
Variable == "Social"  ~ "Social Leadership", Variable == "Lifestyle" ~  "Work and Lifestyle", Variable == "Work" ~  "Work and Lifestyle", Variable == "Perception"~"Experiential",Variable == "Space"~"Experiential", Variable =="Tone"~"Experiential")) %>% filter(!is.na(Dimension))


full2022long$Dimension <- factor(full2022long$Dimension, levels = c("Thinking", "Social Leadership","Work and Lifestyle", "Experiential"))

full2022long$Variable <- factor(full2022long$Variable, levels = c("Analytic","Cognition", "Clout", "Social", "Lifestyle", "Work", "Perception", "Space", "Tone"))
full2022long$reflection = gsub("Exam reflections","Final Exam",full2022long$reflection)

full2022long$reflection <- factor(full2022long$reflection, levels = c("Identifying Barriers", "Youth & Unions", "Women's March","Universal Basic Income & University Tuition", "Final Exam"))


assessments_by_dimension(full2022long)
scores_by_dimension(full2022long, "Thinking", "Social Leadership", "Work and Lifestyle", "Experiential", 0.5, 2.5, 2, 4.3, 4.6, 6.5, 6.4, 9.5)
```

2023
```{r}

full2023long <- full2023long %>% mutate(Dimension = case_when(Variable == "Analytic"~"Thinking", Variable == "Cognition" ~"Thinking", 

Variable == "Clout" ~ "Social Leadership",
Variable == "Social"  ~ "Social Leadership", Variable == "Drives"  ~ "Social Leadership",

Variable == "Lifestyle" ~  "Work and Lifestyle", Variable == "Work" ~  "Work and Lifestyle", 

Variable == "Perception"~"Experiential",Variable == "Space"~"Experiential", Variable =="Authentic"~"Experiential")) %>% filter(!is.na(Dimension))


full2023long$Dimension <- factor(full2023long$Dimension, levels = c("Thinking", "Social Leadership", "Experiential", "Work and Lifestyle"))

full2023long$Variable <- factor(full2023long$Variable, levels = c("Analytic","Cognition", "Clout", "Social","Drives", "Lifestyle", "Work", "Perception", "Space", "Authentic"))

full2023long$reflection <- factor(full2023long$reflection, levels = c("Identifying Barriers", "Youth & Unions", "Women's March","Universal Basic Income & University Tuition", "Final Exam"))


assessments_by_dimension(full2023long)
scores_by_dimension(full2023long, "Thinking", "Social Leadership", "Work and Lifestyle", "Experiential", 0.5, 2.5, 2, 5.5, 5.7, 7.6, 7.4, 10.5)


```

2024
```{r}

full2024long <- full2024long %>% mutate(Dimension = case_when(Variable == "Analytic"~"Thinking (Expressive vs. Analytical Tradeoff)", Variable == "Authentic" ~"Thinking (Expressive vs. Analytical Tradeoff)", 

Variable == "Clout" ~ "Social Leadership",
Variable == "Drives"  ~ "Social Leadership",

Variable == "Lifestyle" ~  "Work and Lifestyle", Variable == "Work" ~  "Work and Lifestyle", 

Variable == "Tone"~"Affective Tone",Variable == "Affect"~"Affective Tone")) %>% filter(!is.na(Dimension))


full2024long$Dimension <- factor(full2024long$Dimension, levels = c("Thinking (Expressive vs. Analytical Tradeoff)", "Social Leadership", "Affective Tone", "Work and Lifestyle"))

full2024long$Variable <- factor(full2024long$Variable, levels = c("Analytic","Authentic", "Clout","Drives", "Lifestyle", "Work", "Tone", "Affect"))

full2024long$reflection <- factor(full2024long$reflection, levels = c("Identifying Barriers", "Youth & Unions", "Women's March","Universal Basic Income and University Tuition","Employer Approaches to Labor Relations", "Final Exam"))

assessments_by_dimension(full2024long)

full2024long %>% filter(!is.na(Score)) %>% group_by(Variable) %>% mutate(mean = mean(Score))  %>% 
ggplot(aes(x = Variable,  y = mean))  + geom_bar(position = "dodge", stat="identity") + labs(title = "", caption = "Percentage of words in student responses that fall into LIWC category.", x = "Dimension",  y ="Mean score")  + theme(legend.position = c(0.8, 0.8)) + ylim(0,105) +
  
  geom_signif(y_position = c(105,100), xmin = c(0.5,2.6), 
              xmax = c(2.4, 4.5), annotation = c("Thinking", "Social Leadership"),
              tip_length = .05)  +
  
  geom_signif(y_position = c(40,70), xmin = c(4.5,6.5), 
              xmax = c(6.4,8.5), annotation = c("Work and Lifestyle", "Affective Tone" ),
              tip_length = .05)
 
```

Affective: This aspect highlights the emotional component, suggesting that the dimension involves emotional responses or feelings.
Tone: This aspect points to the overall mood, quality, or attitude present in communication or experiential settings.

When combined, "Affective Tone" represents the emotional undercurrents or ambiance in a given context, reflecting how emotionality influences the way information is presented or received. It can be used to describe a dimension that measures the general emotional mood or climate of an interaction, communication, or environment.


# Correlation Analyses 
## Extracting leadership scores
### 2022
```{r}
# lead2022 <- leadership_2022 %>% select(c(1, 6, 9:10, 16,17:39, 50:72,83:105,116:138,149:171,182))
# 
# lead2022$rater=lead2022$Name
# 
# lead2022 <- lead2022 %>% 
# unite("ratee1", Q23_2, Q23_1,sep="") %>% mutate(ratee1= tolower(ratee1)) %>% 
# unite("ratee2", Q26_2, Q26_1,sep="") %>% mutate(ratee2= tolower(ratee2)) %>% 
# unite("ratee3", Q30_2, Q30_1,sep="") %>% mutate(ratee3 = tolower(ratee3)) %>% 
# unite("ratee4", Q33_2, Q33_1,sep="") %>% mutate(ratee4 = tolower(ratee4)) %>% 
# unite("ratee5", Q36_2, Q36_1,sep="") %>% mutate(ratee5 = tolower(ratee5))
# 
# write_csv(lead2022,"leadership2022.csv")

lead2022 <- leadership2022 <- read_csv("leadership2022.csv")
lead2022$Q24_1_16 = car::recode(lead2022$Q24_1_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_2_16 = car::recode(lead2022$Q24_2_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_3_16 = car::recode(lead2022$Q24_3_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_4_16 = car::recode(lead2022$Q24_4_16, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_5_16 = car::recode(lead2022$Q24_5_16, '1=5; 2=4; 3=3; 4=2; 5=1')

lead2022$Q24_1_19 = car::recode(lead2022$Q24_1_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_2_19 = car::recode(lead2022$Q24_2_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_3_19 = car::recode(lead2022$Q24_3_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_4_19 = car::recode(lead2022$Q24_4_19, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_5_19 = car::recode(lead2022$Q24_5_19, '1=5; 2=4; 3=3; 4=2; 5=1')

lead2022$Q24_1_20 = car::recode(lead2022$Q24_1_20, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_2_20 = car::recode(lead2022$Q24_2_20, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_3_20 = car::recode(lead2022$Q24_3_20, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_4_20 = car::recode(lead2022$Q24_4_20, '1=5; 2=4; 3=3; 4=2; 5=1')
lead2022$Q24_5_20 = car::recode(lead2022$Q24_5_20, '1=5; 2=4; 3=3; 4=2; 5=1')

pattern_is <- "Q24_[1-5]_[1-10]"
is_columns <- lead2022 %>% select(matches(pattern_is))
lead2022$initiating_structure <- rowMeans(is_columns, na.rm=T)



pattern_cons <-"Q24_[1-5]_(1[1-9]|20)"
cons_columns <- lead2022 %>% select(matches(pattern_cons))
lead2022$consideration<- rowMeans(cons_columns, na.rm=T)
lead2022 <- lead2022  %>% mutate(Ethnicity = case_when(Ethnicity == 1 ~ "Hispanic/Mexican American/Latino/Chicano", 
             Ethnicity ==  2 ~ "White/Caucasian/European-American", 
              Ethnicity ==  3 ~ "Black (African-American, West Indian, Afro-Caribbean)",
              Ethnicity ==  4 ~ "Middle Eastern (Arab, Iranian, Lebanese)", 
              Ethnicity == 5 ~ " South Asian (Indian, Malay, Pakistani)", 
              Ethnicity == 6 ~ "East Asian (Chinese, Korean, Japanese)",
              Ethnicity == 7 ~ "Pacific-Islander (Filipino, Hawaiian)",
              Ethnicity ==  8 ~ "Indigenous")) %>% mutate(Gender = case_when(Gender == 1 ~ "Male", Gender == 2 ~ "Female")) %>% distinct(Name, .keep_all = T)

combined_2022 <- full_liwc_data %>% filter(Year == 2022) %>% right_join(lead2022) %>% rename("Work" = work, "Space" = space) %>% select(Name, Ethnicity, Gender, initiating_structure, consideration,Analytic,Cognition, Clout, Social, Lifestyle, Work, Perception, Space, Tone) 
```

```{r}

# compute correlation matrix
vals2022 <-combined_2022 %>% select(-c(Name,Ethnicity,Gender)) %>% rename("Task Leadership"=initiating_structure, "Interpersonal Leadership" = consideration)
# Desired order of columns
desired_order <- c("Task Leadership", "Interpersonal Leadership" ,"Analytic",
                   "Cognition", "Clout","Social", "Work" , "Lifestyle", "Perception", 
                   "Space" , "Tone"  )

# Reorder columns
vals2022 <- vals2022 %>%
  select(all_of(desired_order))

correlation_matrix<- function(dat){
corr <-cor(dat, use = "complete.obs") 
library(corrplot)
testRes=cor.mtest(vals2022,conf.level=0.95)
p.df = as.data.frame(ggcorrplot::cor_pmat(vals2022))

# p.mat <- cor_mat(allvals)
library(ggcorrplot)

# Function to get asteriks
labs.function = function(x){
  case_when(x > 0.05 ~ "",
            x <= 0.05 & x >= 0.01 ~ "*",
            x < 0.01 & x >= 0.001 ~ "**",
            x < 0.001 ~ "***")
}
# Get asteriks matrix based on p-values
p.labs = p.df  %>%                      
  mutate_all(labs.function)
cor.plot = ggcorrplot(corr, hc.order = F,  type = "lower",
                      lab = TRUE,colors = c("darkgreen","white","orange"),ggtheme = ggplot2::theme_classic)
# Reshaping asteriks matrix to match ggcorrplot data output
p.labs$Var1 = as.factor(rownames(p.labs))
library(data.table)
p.labs = melt(p.labs, id.vars = "Var1", variable.name = "Var2", value.name = "lab")

p.labs$in.df = ifelse(is.na(match(paste0(p.labs$Var1, p.labs$Var2), 
                                  paste0(cor.plot[["data"]]$Var1, cor.plot[["data"]]$Var2))),
                      "No", "Yes")

p.labs = select(filter(p.labs, in.df == "Yes"), -in.df)


# Subsetting asteriks matrix to only those rows within ggcorrplot data
p.labs$in.df = ifelse(is.na(match(paste0(p.labs$Var1, p.labs$Var2), 
                                  paste0(cor.plot[["data"]]$Var1, cor.plot[["data"]]$Var2))),
                      "No", "Yes")

p.labs = select(filter(p.labs, in.df == "Yes"), -in.df)

# Add asteriks to ggcorrplot
cor.plot.labs = cor.plot + 
  geom_text(aes(x = p.labs$Var1, 
                y = p.labs$Var2), 
            label = p.labs$lab, 
            nudge_y = 0.25, 
            size = 5)

cor.plot.labs
}
print(correlation_matrix(vals2022))
ggsave("corrplot2022.png",width=12, height = 12)

```

### 2023
```{r}

lead2023 = read_csv("byRater2023.csv")

data_setup<-function(dat){
columns_needed = c("Name", "Gender", "Ethnicity")
dat <- dat %>% select(columns_needed, matches("Q24"))

substring_to_match <- c("_16", "_19", "_20")
pattern <- paste(substring_to_match, collapse="|")

columns_to_recode = names(dat) %>% .[str_detect(.,pattern)]

dat <- dat %>% mutate_at(vars(one_of(columns_to_recode)), ~car::recode(., '1=5; 2=4; 3=3; 4=2; 5=1'))

pattern_is <- "^Q24_1_([1-9]|10)(_.*)?$"
is_columns <- dat %>%
  select(matches(pattern_is))
dat$initiating_structure <- rowMeans(is_columns, na.rm=T)



pattern_cons <-"Q24_[1-5]_(1[1-9]|20)(_.*)?$"
cons_columns <- dat %>% select(matches(pattern_cons))
dat$consideration<- rowMeans(cons_columns, na.rm=T)
dat <- dat%>% distinct(Name, .keep_all = T)
}

lead2023 <- data_setup(lead2023)

combined_2023 <- full_liwc_data %>% filter(Year == 2023) %>% right_join(lead2023) %>% rename("Work" = work, "Space" = space) %>% select(Name, Ethnicity, Gender, initiating_structure, consideration,Analytic,Cognition, Clout, Social,Drives, Lifestyle, Work, Perception, Space, Authentic) 
```

```{r}

# compute correlation matrix
vals2023 <-combined_2023 %>% select(-c(Name,Ethnicity,Gender)) %>% rename("Task Leadership"=initiating_structure, "Interpersonal Leadership" = consideration)
# Desired order of columns
desired_order <- c("Task Leadership", "Interpersonal Leadership" ,"Analytic","Cognition", "Clout", "Social","Drives", "Lifestyle", "Work", "Perception", "Space", "Authentic"  )

# Reorder columns
vals2023 <- vals2023 %>%
  select(all_of(desired_order))

correlation_matrix<- function(dat){
corr <-cor(dat, use = "complete.obs") 
library(corrplot)
testRes=cor.mtest(dat,conf.level=0.95)
p.df = as.data.frame(ggcorrplot::cor_pmat(dat))

# p.mat <- cor_mat(allvals)
library(ggcorrplot)

# Function to get asteriks
labs.function = function(x){
  case_when(x > 0.05 ~ "",
            x <= 0.05 & x >= 0.01 ~ "*",
            x < 0.01 & x >= 0.001 ~ "**",
            x < 0.001 ~ "***")
}
# Get asteriks matrix based on p-values
p.labs = p.df  %>%                      
  mutate_all(labs.function)
cor.plot = ggcorrplot(corr, hc.order = F,ggtheme = ggplot2::theme_classic, type = "lower",
                      lab = TRUE,colors = c("darkgreen","white","orange"))
# Reshaping asteriks matrix to match ggcorrplot data output
p.labs$Var1 = as.factor(rownames(p.labs))
library(data.table)
p.labs = melt(p.labs, id.vars = "Var1", variable.name = "Var2", value.name = "lab")

p.labs$in.df = ifelse(is.na(match(paste0(p.labs$Var1, p.labs$Var2), 
                                  paste0(cor.plot[["data"]]$Var1, cor.plot[["data"]]$Var2))),
                      "No", "Yes")

p.labs = select(filter(p.labs, in.df == "Yes"), -in.df)


# Subsetting asteriks matrix to only those rows within ggcorrplot data
p.labs$in.df = ifelse(is.na(match(paste0(p.labs$Var1, p.labs$Var2), 
                                  paste0(cor.plot[["data"]]$Var1, cor.plot[["data"]]$Var2))),
                      "No", "Yes")

p.labs = select(filter(p.labs, in.df == "Yes"), -in.df)

# Add asteriks to ggcorrplot
cor.plot.labs = cor.plot + 
  geom_text(aes(x = p.labs$Var1, 
                y = p.labs$Var2), 
            label = p.labs$lab, 
            nudge_y = 0.25, 
            size = 5)

cor.plot.labs
}
print(correlation_matrix(vals2023))
ggsave("corrplot2023.png",width=12, height = 12)

```

### 2024
```{r}
lead2024 = read_csv("byRater2024.csv")

data_setup<-function(dat){
columns_needed = c("Name", "Gender", "Ethnicity")
dat <- dat %>% select(columns_needed, matches("Q24"))

substring_to_match <- c("_16", "_19", "_20")
pattern <- paste(substring_to_match, collapse="|")

columns_to_recode = names(dat) %>% .[str_detect(.,pattern)]

dat <- dat %>% mutate_at(vars(one_of(columns_to_recode)), ~car::recode(., '1=5; 2=4; 3=3; 4=2; 5=1'))

pattern_is <- "^Q24_1_([1-9]|10)(_.*)?$"
is_columns <- dat %>%
  select(matches(pattern_is))
dat$initiating_structure <- rowMeans(is_columns, na.rm=T)



pattern_cons <-"Q24_[1-5]_(1[1-9]|20)(_.*)?$"
cons_columns <- dat %>% select(matches(pattern_cons))
dat$consideration<- rowMeans(cons_columns, na.rm=T)
dat <- dat%>% distinct(Name, .keep_all = T)
}

lead2024 <- data_setup(lead2024)

combined_2024 <- full_liwc_data %>% filter(Year == 2024) %>% right_join(lead2024) %>% rename("Work" = work, "Space" = space) %>% select(Name, Ethnicity, Gender, initiating_structure, consideration,Analytic,Authentic, Clout,Drives, Lifestyle, Work, Tone, Affect) 
```

```{r}

# compute correlation matrix
vals2024 <-combined_2024 %>% select(-c(Name,Ethnicity,Gender)) %>% rename("Task Leadership"=initiating_structure, "Interpersonal Leadership" = consideration)
# Desired order of columns
desired_order <- c("Task Leadership", "Interpersonal Leadership" ,"Analytic","Authentic", "Clout","Drives", "Lifestyle", "Work", "Tone", "Affect" )

# Reorder columns
vals2024 <- vals2024 %>%
  select(all_of(desired_order))

correlation_matrix<- function(dat){
corr <-cor(dat, use = "complete.obs") 
library(corrplot)
testRes=cor.mtest(dat,conf.level=0.95)
p.df = as.data.frame(ggcorrplot::cor_pmat(dat))

# p.mat <- cor_mat(allvals)
library(ggcorrplot)

# Function to get asteriks
labs.function = function(x){
  case_when(x > 0.05 ~ "",
            x <= 0.05 & x >= 0.01 ~ "*",
            x < 0.01 & x >= 0.001 ~ "**",
            x < 0.001 ~ "***")
}
# Get asteriks matrix based on p-values
p.labs = p.df  %>%                      
  mutate_all(labs.function)
cor.plot = ggcorrplot(corr, hc.order = F, ggtheme = ggplot2::theme_classic,type = "lower",
                      lab = TRUE,colors = c("darkgreen","white","orange"))
# Reshaping asteriks matrix to match ggcorrplot data output
p.labs$Var1 = as.factor(rownames(p.labs))
library(data.table)
p.labs = melt(p.labs, id.vars = "Var1", variable.name = "Var2", value.name = "lab")

p.labs$in.df = ifelse(is.na(match(paste0(p.labs$Var1, p.labs$Var2), 
                                  paste0(cor.plot[["data"]]$Var1, cor.plot[["data"]]$Var2))),
                      "No", "Yes")

p.labs = select(filter(p.labs, in.df == "Yes"), -in.df)


# Subsetting asteriks matrix to only those rows within ggcorrplot data
p.labs$in.df = ifelse(is.na(match(paste0(p.labs$Var1, p.labs$Var2), 
                                  paste0(cor.plot[["data"]]$Var1, cor.plot[["data"]]$Var2))),
                      "No", "Yes")

p.labs = select(filter(p.labs, in.df == "Yes"), -in.df)

# Add asteriks to ggcorrplot
cor.plot.labs = cor.plot + 
  geom_text(aes(x = p.labs$Var1, 
                y = p.labs$Var2), 
            label = p.labs$lab, 
            nudge_y = 0.25, 
            size = 5)

cor.plot.labs
}
print(correlation_matrix(vals2024))
ggsave("corrplot2024.png",width=12, height = 12)

```


# Differences in Groups
```{r}
fulllong2022 <- data_year_longer(full_liwc_data, 2022) %>% full_join(class_2022) %>% mutate(Dimension = case_when(Variable == "Analytic"~"Thinking",
Variable == "Cognition" ~"Thinking", Variable == "Clout" ~ "Social Leadership",
Variable == "Social"  ~ "Social Leadership", Variable == "Lifestyle" ~  "Work and Lifestyle", Variable == "Work" ~  "Work and Lifestyle", Variable == "Perception"~"Experiential",Variable == "Space"~"Experiential", Variable =="Tone"~"Experiential")) %>% filter(!is.na(Dimension)) %>% filter(!is.na(Gender))

fulllong2023 <- data_year_longer(full_liwc_data,2023) %>% left_join(class_2023,by="Name") %>% mutate(Dimension = case_when(Variable == "Analytic"~"Thinking", Variable == "Cognition" ~"Thinking", 

Variable == "Clout" ~ "Social Leadership",
Variable == "Social"  ~ "Social Leadership", Variable == "Drives"  ~ "Social Leadership",

Variable == "Lifestyle" ~  "Work and Lifestyle", Variable == "Work" ~  "Work and Lifestyle", 

Variable == "Perception"~"Experiential",Variable == "Space"~"Experiential", Variable =="Authentic"~"Experiential")) %>%  filter(!is.na(Dimension))


fulllong2024 <-data_year_longer(full_liwc_data,2024)  %>% left_join(class_2024,by="Name") %>% mutate(Dimension = case_when(Variable == "Analytic"~"Thinking", Variable == "Authentic" ~"Thinking", 

Variable == "Clout" ~ "Social Leadership",
Variable == "Drives"  ~ "Social Leadership",

Variable == "Lifestyle" ~  "Work and Lifestyle", Variable == "Work" ~  "Work and Lifestyle", 

Variable == "Tone"~"Affective Tone",Variable == "Affect"~"Affective Tone")) %>% filter(!is.na(Dimension)) %>%mutate(reflection= factor(reflection, levels = c("Identifying Barriers", "Youth & Unions", "Women's March","Universal Basic Income and University Tuition","Employer Approaches to Labor Relations", "Final Exam"))) %>% filter(!is.na(Gender))
library(sjstats)
library(rstatix)
assessments_by_dimension_by_Sex <- function(dat,dimension){
dat  %>% filter(Dimension == "Thinking") %>% ggplot(aes(x=Gender,y=Score, fill=Gender)) + geom_boxplot() + facet_wrap(Dimension~reflection,nrow = 1)+
labs(x="Assessment",y="Mean Dimension Score") + theme(legend.position = "right", axis.text.x = element_text(angle = 30,hjust = 1))}

# Required libraries
library(dplyr)
library(broom)
library(purrr)
variables <- unique(fulllong2023$Variable)

# Function to compute ANOVA and tidy the results
compute_anova <- function(var) {
  dt <- fulllong2024 %>% filter(Variable == var)
  # Perform ANOVA and tidy the output
  tidy_results <- aov(Score ~ reflection * Gender, data = dt) %>%
    broom::tidy()
  
  # Add variable name to the results
  tidy_results$Variable <- var
  
  return(tidy_results)
}

# Compute ANOVA for each variable and create a summary table
anova_summary <- map_df(variables, compute_anova)

# Display the summary table
anova_summary %>% kable()

assessments_by_dimension_by_Sex(fulllong2024)


ggsave("dim_by_sex2024.png",width=14,height=14)
  


```

